%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[super]{nth}
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[scale=0.9]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{1.7cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Jay} % Your first name
\familyname{Anwar} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}
\address{}{London, UK}
\mobile{07925 357505}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{j.anwar95@gmail.com}
% \homepage{github.com/jayanwar}{github.com/jayanwar}

%\extrainfo{additional information}
%\photo[70pt][0.4pt]{picture} % The first bracket is the picture height, the second is %the thickness of the frame around the picture (0pt for no frame)

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}
\cventry{{\footnotesize NOV 2021--}}{Full Stack Developer}{BNY Mellon}{London}{}{
    \begin{itemize}
        \item Front office developer role working in TypeScript and Java to build and maintain applications central to the running of the FX sales and trading platform.
        \item Migration of legacy codebase from JavaScript to TypeScript to build a new frontend for the FX Trading Platforms.
        \item Liaise with stakeholders in locations around the world in order to resolve issues and implement features.
    \end{itemize}
}
\cventry{{\footnotesize SEP 2019--SEP 2021}}{Developer}{Space48}{Manchester}{}{
    \begin{itemize}
        \item Worked closely with external clients to deliver integration apps and micro-services to meet their business requirements, running demos and conducting end-to-end tests.
        \item Integrated SaaS platforms with the use of cloud architecture (Microsoft Azure/Google Cloud).
    \end{itemize}
}
\cventry{{\footnotesize JUN--JUL 2019}}{Teaching Intern}{Loreto College/St Peter's RC}{Manchester}{}{
    \begin{itemize}
        \item Acted as a teaching assistant in high school classes of mixed ability whilst also putting together and leading a Maths Roadshow type session (problem solving type problems, fixed amount of time to try and solve).
    \end{itemize}
}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{{\footnotesize 2015--2019}}{Mathematics MMath(Hons)}{University of Manchester, UK}{}{\nth{1} Class}{}  % Arguments not required can be left empty

\cventry{{\footnotesize 2014--2015}}{Foundation Year (Science and Engineering)}{University of Manchester, UK}{}{84\%}{}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{Notable Projects}
\cventry{{\footnotesize 2022}}{App Migration}{BNY Mellon}{Internal Trade Enrichment Tool}{}{
    \begin{itemize}
        \item Rebuilt an internal tool's frontend codebase in Angular after AngularJS (1.x) EOL, as part of a team with members in the UK, India and the US.
        \item Joined midway through the project and quickly became a contributing member of the team, optimising existing build processes and the developer experience.
        \item Documented the existing functionality of the app and noted parts of the architecture (both frontend and backend) which could be improved upon.
    \end{itemize}
}
\cventry{{\footnotesize 2020-2021}}{App Development}{Space48}{Styla CMS Shopify App}{}{
\begin{itemize}
\item Worked in a team of 3 to architect and develop a Shopify app - from receiving client requirements to developing a build available to Shopify merchants. App is responsible for syncing pages periodically from a CMS platform to a Shopify store, allowing those pages to be viewable on the store without human interaction
\item Use NextJS (a React framework) to build a full stack app, which is deployed to GCP as an App engine project, using Firestore as a database.
\item Tackled both frontend and backend aspects of the app. Frontend required the development of a single page UI which lists Styla pages and their sync status. Backend required the development of the periodic sync process.
\end{itemize}
}

\cventry{{\footnotesize 2019-2020}}{Website Re-platform}{Space48}{Ordnance Survey Map Shop}{}{
\begin{itemize}
\item Major project in terms of size and scope, re-platforming a client's website from Magento to BigCommerce.
\item Personally built 5(out of a total 6) of the integration micro-services using Microsoft Azure, including Single Sign-On (SSO) integration and subscription services. 
\item Took a leading role in the development of the subscription service, taking responsibility for architectural design, writing of test plans, user/support documentation and client demos. 
\item Used teamwork and presentation skills in a project team spanning three organisations, with demos attended by up to 30 stakeholders.
\end{itemize}
}

\cventry{{\footnotesize 2018--2019}}{Regular Graphs and Constructions of Cages}{University of Manchester}{Master's Thesis (Grade: 85\%)}{}{
\begin{itemize}
    \item Researched techniques for constructing graphs with specific properties, finding the minimum number of vertices needed for a graph with these properties using the algebraic software package Magma.
    \item Utilised a graph-theoretic approach, describing algorithms from an abstract algebra perspective.
\end{itemize}
}  % Arguments not required can be left empty

\cventry{{\footnotesize 2018}}{Sorting Algorithms and the Game of Life}{University of Manchester}{4th Year Module (Grade: 85\%)}{}{
\begin{itemize} 
    \item Wrote a program to simulate John Conway's \textit{Game of Life} in C++, making extensive use of sorting functions and recursion, as well as the core object-oriented features of classes such as inheritance and abstraction.
\end{itemize}
}

\cventry{{\footnotesize 2017}}{Connect 4}{University of Manchester}{2nd Year Module (Grade: 92\%)}{}{
\begin{itemize}
    \item Wrote a command line Connect 4 game in Python, allowing the user to play against another human, the computer, or run a game between two computer opponents.
\end{itemize}
}


%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}

\cvitem{{\footnotesize Programming Languages}}{TypeScript/JavaScript, Python, Bash/Shell, Java, C++, PHP, HTML, Matlab {\footnotesize (basic)}, R {\footnotesize (basic)}}
\cvitem{{\footnotesize Frameworks}}{\textbf{\textit{Frontend}}: React, Angular, NextJS; \textbf{\textit{Backend}}: Express, Koa, Spring}
\cvitem{{\footnotesize Databases}}{Microsoft Azure Cosmos {\footnotesize (similar to MongoDB)}, Google Firestore {\footnotesize (NoSQL)}, Microsoft SQL Server}
\cvitem{{\footnotesize General Computing}}{Linux {\footnotesize (Ubuntu, Raspbian/Debian, QNAP OS)}, Docker, \LaTeX}

%\cvitem{General}{Public speaking, simplifying abstract/advanced concepts.}


%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

%\section{Languages}
%\begin{small}
%\cvitemwithcomment{Arabic}{Native Speaker}{}
%\cvitemwithcomment{French}{Near Native}{excellent command}
%\cvitemwithcomment{English}{Near Native}{excellent command}
%\cvitemwithcomment{Chinese}{Intermediate}{good working %knowledge}
%\cvitemwithcomment{Japanese}{Intermediate}{good working %knowledge}
%\end{small}


%----------------------------------------------------------------------------------------
%	INTERESTS AND EXTRA CURRICULAR ACTIVITY SECTION
%----------------------------------------------------------------------------------------
%\bigskip



%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}